Case for Support

### 2021-11-16 application/detailsOfResource.tex

We intend to improve an \textbf{existing resource}, the Bonsai ecosystem. We
propose to create software infrastructure to facilitate the integration into
Bonsai
of existing advanced data analysis methods
(Section~\ref{sec:infrastructure}).
%
To demonstrate the use of this infrastructure, and to provide Bonsai users with
an initial set of advanced machine intelligence neural data analysis methods,
we will add to the Bonsai ecosystem machine learning functionality to control
neuroscience experiments and to analyse data generated by them
(Section~\ref{sec:functionality}).

This initial set of methods should demonstrate to Bonsai users, and to
machine-learning methods developers, the potential of embedding
machine-learning functionality into the experimental control loop. We propose
user engagement activities to expose both of these groups of people to this
potential (Section~\ref{sec:userEngagement}).  When data-analysis method
developers recognise this potentials, they will become interested in
contributing their methods to the Bonsai ecosystem, ensuring the
\textbf{long-term sustainability} of the proposed resource.

>>>>

We intend to improve an \textbf{existing resource}, the Bonsai ecosystem. We
propose to create software infrastructure to enable the\textbf{ integration of advanced data analysis methods} into
Bonsai (Section~\ref{sec:infrastructure}).
%
To demonstrate the use of this infrastructure, and to provide Bonsai users with
an initial set of advanced machine intelligence neural data analysis methods,
we will add to the Bonsai ecosystem machine learning functionality to control
neuroscience experiments and to analyse data generated by them
(Section~\ref{sec:functionality}).

This initial set of methods should demonstrate to Bonsai users, and to
machine-learning methods developers, the potential of embedding
machine-learning functionality into the experimental control loop. We propose
user engagement activities to expose both of these groups to this
potential (Section~\ref{sec:userEngagement}).  As data-analysis method
developers recognise this opportunity, they will become interested in
contributing their methods to the Bonsai ecosystem, ensuring the
\textbf{long-term sustainability} of the proposed resource.
